QPLIB: A Library of Quadratic Programming Instances

### 2018-02-01 QPLIB-2.1.tex
{\textstyle \half}
Update QPLIB-2.1.tex

In mathematical optimization, a Quadratic Program (QP) is an optimization problem in which either the objective function, or some of the constraints, or both, are quadratic functions. More specifically, the problem has the form
%
\begin{align*}
 \min \textrm{or} \max \;\;
 & \half x^\top Q^0 x + b^0 x + q^0 \\
 \textrm{such that}\;\;
 & c^i_l \leq \half x^\top Q^i x + b^i x \leq c^i_u & i \in \Mcm, \\
 %
 & l_j \leq x_j \leq u_j & j \in \Mcn,  \\
 %
 \textrm{and}\;\;
 & x_j \in \mathbb{Z} & j \in \Mcz,
\end{align*}
%
%\begin{align*}
% \min \;\;
% & x^\top Q^0 x + b^0 x \\
% %
% & x^\top Q^i x + b^i x \leq c^i & i \in \Mcm \\
% %
% & l_j \leq x_j \leq u_j & j \in \Mcn  \\
% %
% & x_j \in \mathbb{Z} & j \in \Mcz
%\end{align*}
%
where
%
\begin{itemize}
 \item $\Mcn = \{ 1, \ldots, n \}$ is the set of (indices) of variables, and $\Mcm = \{ 1, \ldots, m \}$ is the set of (indices) of constraints;
 %
 \item $x = [x_j]_{j = 1}^n$ %\in \RR^n$
is a finite vector of real variables;
 %
 \item $Q^i$ for $i \in \{ 0 \} \cup \Mcm$ are symmetric $n \times n$ real (Hessian) matrices: since one is only interested in the value of quadratic forms of the type $x^\top Q^i x$, symmetry can be assumed without loss of generality by just replacing off diagonal pairs $Q^i_{hk}$ and $Q^i_{kh}$ with their average $(Q^i_{hk} + Q^i_{kh}) / 2$;
 %
 \item $b^i$, $c_u^i$, $c_l^i$ for $i \in \{ 0 \} \cup \Mcm$, and $q^0$ are, respectively, real $n$-vectors and real constants;
 %
 \item $-\infty \leq l_j \leq u_j \leq \infty$ are the (extended) real lower and upper bounds on each variable $x_j$ for $j \in \Mcn$;
 %
 \item $\Mcm = \Mcq \cup \Mcl$ where $Q^i = 0$ for all $i \in \Mcl$ (i.e., these are the linear constraints, as opposed to the truly quadratic ones); and
 %
 \item the variables in $\Mcz \subseteq \Mcm$ are restricted to only attain integer values.
\end{itemize}
%
Due to the presence of integrality requirements on the variables and of quadratic constraints, this class of problems is often referred to as Mixed-Integer Quadratically Constraint Quadratic Program (MIQCQP). It will be sometimes useful to refer to the (sub)set $\Mcb =  \{ \, j \in \Mcz : l_j = 0 , u_j = 1 \, \} \subseteq \Mcz$ of the binary variables, and to $\Mcr = \Mcn \setminus \Mcz$ as the set of continuous ones. Similarly, it will be sometimes useful to distinguish the (sub)set $\Mcx = \{ \, j : l_j > -\infty \lor u_j < \infty \, \}$ of the box-constrained variables from $\Mcu = \Mcn \setminus \Mcx$ of the unconstrained ones (in the sense that finite bounds are not explicitly provided in the data of the problem, although they may be implied by the other constraints).

@@

>>>>

In mathematical optimization, a Quadratic Program (QP) is an optimization problem in which either the objective function, or some of the constraints, or both, are quadratic functions. More specifically, the problem has the form
%
\begin{align*}
 \min \textrm{or} \max \;\;
 & {\textstyle \half} x^\top Q^0 x + b^0 x + q^0 \\
 \textrm{such that}\;\;
 & c^i_l \leq {\textstyle \half} x^\top Q^i x + b^i x \leq c^i_u & i \in \Mcm, \\
 %
 & l_j \leq x_j \leq u_j & j \in \Mcn,  \\
 %
 \textrm{and}\;\;
 & x_j \in \mathbb{Z} & j \in \Mcz,
\end{align*}
%
%\begin{align*}
% \min \;\;
% & x^\top Q^0 x + b^0 x \\
% %
% & x^\top Q^i x + b^i x \leq c^i & i \in \Mcm \\
% %
% & l_j \leq x_j \leq u_j & j \in \Mcn  \\
% %
% & x_j \in \mathbb{Z} & j \in \Mcz
%\end{align*}
%
where
%
\begin{itemize}
 \item $\Mcn = \{ 1, \ldots, n \}$ is the set of (indices) of variables, and $\Mcm = \{ 1, \ldots, m \}$ is the set of (indices) of constraints;
 %
 \item $x = [x_j]_{j = 1}^n$ %\in \RR^n$
is a finite vector of real variables;
 %
 \item $Q^i$ for $i \in \{ 0 \} \cup \Mcm$ are symmetric $n \times n$ real (Hessian) matrices: since one is only interested in the value of quadratic forms of the type $x^\top Q^i x$, symmetry can be assumed without loss of generality by just replacing off diagonal pairs $Q^i_{hk}$ and $Q^i_{kh}$ with their average $(Q^i_{hk} + Q^i_{kh}) / 2$;
 %
 \item $b^i$, $c_u^i$, $c_l^i$ for $i \in \{ 0 \} \cup \Mcm$, and $q^0$ are, respectively, real $n$-vectors and real constants;
 %
 \item $-\infty \leq l_j \leq u_j \leq \infty$ are the (extended) real lower and upper bounds on each variable $x_j$ for $j \in \Mcn$;
 %
 \item $\Mcm = \Mcq \cup \Mcl$ where $Q^i = 0$ for all $i \in \Mcl$ (i.e., these are the linear constraints, as opposed to the truly quadratic ones); and
 %
 \item the variables in $\Mcz \subseteq \Mcm$ are restricted to only attain integer values.
\end{itemize}
%
Due to the presence of integrality requirements on the variables and of quadratic constraints, this class of problems is often referred to as Mixed-Integer Quadratically Constraint Quadratic Program (MIQCQP). It will be sometimes useful to refer to the (sub)set $\Mcb =  \{ \, j \in \Mcz : l_j = 0 , u_j = 1 \, \} \subseteq \Mcz$ of the binary variables, and to $\Mcr = \Mcn \setminus \Mcz$ as the set of continuous ones. Similarly, it will be sometimes useful to distinguish the (sub)set $\Mcx = \{ \, j : l_j > -\infty \lor u_j < \infty \, \}$ of the box-constrained variables from $\Mcu = \Mcn \setminus \Mcx$ of the unconstrained ones (in the sense that finite bounds are not explicitly provided in the data of the problem, although they may be implied by the other constraints).

@@

\textcolor{red}{In the rest of this paper, we shall sometimes refer to {\it exact solutions} of quadratic programs. In view of the fact that their solutions may be irrational, this notation deserves a comment. If the decision version of the problem being referred to is in NP (e.g.~LP, MILP, QP \cite{vavasis90a}), then the assumption is that all rational numbers can be represented exactly by a Turing Machine (TM). 
%This assumption has the same limitation as the assumption that TMs defined on integers are a faithful abstraction of a real computer, namely that the range of integers needing a representation is bounded. 
If there is no known proof that the problem being solved (or its decision version) is in NP, then there are four main approaches:
\begin{enumerate}
\item finding a representable solution $x'$ such that $\|x'-x^\ast\|_\infty\le\varepsilon$, where $x^\ast$ is the true solution, $\varepsilon>0$ is given, and representable means having a polynomially sized description length
% ``
(in function of the instance size) \cite{hochbaum2};
\item using the {\it Thom encoding} of an algebraic number \cite[Prop.~2.28]{pollack} (limited to problems involving polynomials);
\item using the optimality gap: finding a representable solution $x'$ such that $|f(x')-f(x^\ast)|\le\varepsilon$, where $f$ is the objective function, $x^\ast$ is the true solution, $\varepsilon>0$ is given
%, and representable is as above 
(limited to optimization problems);\label{optgap}
\item using a computational model according to which every elementary computation on the reals takes $O(1)$ and returns a precise result \cite[p.~24]{blum}.
\end{enumerate}
Approach \ref{optgap} in the list above is the one most often used in computational papers, including the present one.}
